---
title: "FRRO2Compare"
author:
- Douglas A. Campbell
- Maximilian Berthold
output:
  html_document:
    df_print: paged
    code_folding: hide
    keep_md: yes
    fig_caption: yes
    toc: TRUE
    toc_float: TRUE
csl: plos-one.csl
---

# Introduction
Compare [O2] to FRRf data for a dataset.

Define time windows defined by changes in PAR imposed by script from FRRf changes in PAR.
For each run create a series of nests of [O2] data from optode for each PAR level and each TempCont setting.
Trim [O2] data nests to remove first 35 rows (~ 35 s) of 180 rows (~ 180 s) to avoid initial induction period.
Fit slopes of umol O2  l~-1~ s~-1~ for each PAR level nest.
Generate estimates of gross umol O2  l~-1~ s~-1~ by subtracting dark respiration rates.
  Initial and final O2 respiration rate estimators; average? chose?
  
  
## Set Chunk Options
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```


```{r set general project variables}
#"..", takes up a level in the directory path
Project <- "FluorO2"

DataInO2 <- file.path("..","ImportData", "Optode")
DataInFRRf <- file.path("..","ImportData", "FRRf")
DataOut <- file.path("..", "FitData")
#CatalogPath <- file.path("../MURIS/MURIS_catalog.csv")
CatalogURL <- "https://docs.google.com/spreadsheets/d/1ZXpwR7Gfto-uRzVdXzMpQF4frbrvMLH_IyLqonFZRSw/edit#gid=0"

Run <- "SySlCCACaloxy"

```


```{r set constants}
photons_umol = 6.022E17
A2_m2 = 1E20
us_s = 1000000
```


```{r load libraries} 
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
library(broom)
#library(knitr)
#library(zoo)
library(googlesheets4)
library(googledrive)
```


```{r set colours}
Wavelengths_nm = c(445, 470, 505, 535, 590)
Colours_nm = c("darkblue", "dodgerblue", "darkgreen", "yellowgreen",  "darkorange")


names(Colours_nm) <- Wavelengths_nm
Colours_nm

```


This chunk reads in a MetaData catalog from googlesheets
Optode Data already merged with MetaData but workflow needs a re-merger.
```{r load Catalog, now as a google sheet}
gs4_deauth()

MetaData <- read_sheet(CatalogURL) %>%
   drop_na(WL) %>%
   mutate(WL = unlist(WL))
 
 as.data.frame(MetaData)




```


```{r read FRRf data across all runs}
#Temporary RunDate during auditing
#Run <- "SySlCCACaloxy"
FRRfData <- readRDS(file = file.path(DataInFRRf, paste("FluorO2_", Run, "_SolFitsTrim.Rds", sep = "")))

head(FRRfData)
```


# Set Run Specific Variables for each set of O2 Data; TC/noTC, RunDateOxy, StrainID

```{r set run specific O2 variables}
  #FRRf refit includes data from both dates
#RunDateOxy <- 20211210
  #20211213 alternate date
Cuvette <- "TC"
#StrainID <- "MaBe3729"

```


#Filter FRRf data to match selected O2 data
```{r filter FRRfData}
FRRfDataLight <- FRRfData %>%
  filter(!is.na(LR_s)) %>%
  filter(TempCont == Cuvette) %>%
  #filter(CultureID == StrainID) %>%
  filter(Dark1s == 0)

#%>%
#  filter(ObsDate == ymd(RunDateOxy))

```

Read in Run Specific O2Data
Make this more general as we accumulate more files.
```{r read data}
#temporary hack to cope with run date; replace with GREP? or map?
O2Data <- readRDS(file = file.path(DataInO2, paste("FluorO2_", Run, "_O2Data.Rds", sep = "")))

head(O2Data)
```


Remove missing rows, reconcile time formats
```{r remove missing rows}
O2Data <- O2Data %>%
  filter(!is.na(LR_s))

#%>%
  #filter(CultureID == StrainID) %>%
  #mutate(ObsDate = ymd(RunDate),
   #      ObsTime = as.period(AbsTime),
    #     Ex_WL = as.factor(Ex_WL))

head(O2Data)

O2Data <- O2Data %>%
  mutate(TempCont = "TC")
```

```{r prelimplot O2}
O2Data %>%
  ggplot() +
  geom_point(aes(x = LR_s, y = O2_umolL, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(rows = vars(CultureID), cols = vars(Ex_WL)) +
  xlim(0, 1000) +
  theme(strip.text.y = element_text(size = 5, angle=0)) +
  scale_y_continuous(sec.axis = sec_axis(~ . , name = "CultureID", breaks = NULL, labels = NULL)) +
  scale_x_continuous(sec.axis = sec_axis(~ . , name = "Ex_WL", breaks = NULL, labels = NULL)) +
  coord_cartesian(xlim = c(0, 1200))

```

Draw plot from two dataframes
```{r two dataframe plot}
ggplot() +
  geom_point(data = O2Data, aes(x = LR_s, y = O2_umolL, colour = Ex_WL)) +
  geom_point(data = FRRfDataLight, aes(x = LR_s, y = ETRCtauav), colour = "black") +
  facet_grid(rows = vars(CultureID), cols = vars(Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  coord_cartesian(xlim = c(0, 1200))
```




```{r leftjoin}
colnames(O2Data)
colnames(FRRfDataLight)

O2SlopeData <- left_join(x = O2Data, y = FRRfDataLight, by = c("Project", "Run", "CultureID", "Ex_WL", "GrowthLight", "TempCont", "Date" = "ObsDate","LR_s"), suffix = c("O2", "FRRf"), keep = FALSE)

head(O2SlopeData)
```