---
title: "O2ImportTidyTutorial"
author:

- Douglas A. Campbell
- Maximilian Berthold
- Laurel Genge
output:
  html_document:
    df_print: paged
    code_folding: hide
    keep_md: yes
    fig_caption: yes
    toc: TRUE
    toc_float: TRUE
csl: plos-one.csl
---

# Introduction
We use an optode to measure [O2] µmol l-1 in suspensions of phytoplankton.
Changes in [O2] reflect (hopefully) oxygen evolution or oxygen consumption by the cell suspension.

# Materials and Methods

This .Rmd Rworkbook imports multiple parallel data files in simple .txt .tsv form exported from FireSting optodes based upon project specific values for variables set by the user.

It tidies and organizes the data.

 
# Set Chunk Options
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

```{r set project variables}

Project <- "FluorO2"

Run <- "SySlCCACaloxy"

FileID <- "caloxy"
DataIn <- file.path("..", "RawData", "Optode", Run)

DataOut <- file.path("..", "ImportData", "Optode")

FileEncode <- "UTF-8"
Delimiter <- "\t"

HeaderRows <- 13
Comment <- "#"

#Set URL for MetaData
MetaDataURL <- "https://docs.google.com/spreadsheets/d/1ZXpwR7Gfto-uRzVdXzMpQF4frbrvMLH_IyLqonFZRSw/edit#gid=0"


```

```{r load libraries} 
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
library(broom)
library(googlesheets4)
library(googledrive)

#library(knitr)
#library(zoo)
#library(tidyquant)
```


```{r set colours}
#Setting a vector of wavelength values, then using it to 'name' a vector of R colour values will allow us to assign colours to wavelengths later
Wavelengths_nm = c(445, 470, 505, 535, 590)
Colours_nm = c("darkblue", "dodgerblue", "darkgreen", "yellowgreen",  "darkorange")


names(Colours_nm) <- Wavelengths_nm
Colours_nm


```

Read in MetaData catalog
```{r load catalog from googlesheet}

gs4_deauth() #deauthorizes access to googlesheet

MetaDataCatalog <- read_sheet(MetaDataURL) %>%
  drop_na(WL) %>%
  mutate(WL = unlist(WL))

# # sheet is read in by sheet ID, obtained from the URL of the sheet.
# # read_sheet sets the type of columns it can't parse to a list.
# # ggplot/dplyr does not work well with a dataframe of lists.
# # In this case WL is set to a list since some values are numbers, some are strings, some are blank.
# # To fix this, first drop all rows missing WL, then unlist.
# # Must first drop NA rows since unlist will collapse NULL lists, then the unlisted WL is a shorter length than original WL column, which mutate doesn't like.
# 
 
 head(as.data.frame(MetaDataCatalog))
```

List O2 data files
```{r O2Data files}

O2DataFiles <- list.files(path = DataIn, pattern = FileID, full.names = TRUE, recursive = FALSE)

O2DataFiles

O2DataFiles <-  grep('txt', O2DataFiles, value = TRUE, invert = FALSE)

#only retain .txt files
length(O2DataFiles)
O2DataFiles

```

We have a path to a folder that contains `r length(O2DataFiles)` saved in the .txt format we seek.
This data set is big enough to be worth a bulk import, but small enough to handle.

Create function read_tsv_plus adding file name and skips header rows to start reading file after string "Data" read.delim_plus or read_delim_plus adds filename and cdate, message=FALSE, warning=FALSE

```{r create function to read data}
read_delim_plus <- function(flnm, delimiter, headerrows, fileencode){read_delim(flnm, delim = delimiter,  col_names = TRUE,  comment = Comment, skip = headerrows, escape_double = FALSE,  locale = locale(encoding = fileencode), trim_ws = TRUE) %>%
    mutate(Filename = flnm,
           Cdatetime = ymd_hms(file.info(flnm)$ctime))
  }
```

```{r read optode data}

# test <- c(1,2,3)
# 
# bob <- test %>%
#   map(~. + 1)

#tidy after map_df
O2Data <- O2DataFiles %>%
  map_df(~read_delim_plus(flnm = ., delimiter = Delimiter, headerrows = HeaderRows, fileencode = FileEncode)) %>%
  select(
    where(
      ~!all(is.na(.x)) #remove columns of all na
    )
  ) %>%
  select(
    where(
      ~!all(str_detect(.x, pattern = "---")) #remove columns containing only all "---"
    )
  ) %>%
  select(-c(`(mbar)`, `(%)`,`('C)...15`,`Ch 1...18`,`Ch1...22`,`Ch1...26`)) %>%
  rename(Time_hms = `Time (HH:MM:SS)`,
         LR_s = `Time (s)`,
         O2_umolL = `Ch1...5`,
         Temp_C = `Ch 1...9`)

#tidy inside map_df seems slower
# O2Data2 <- O2DataFiles %>%
#   map_df(~read_delim_plus(flnm = ., delimiter = Delimiter, headerrows = HeaderRows, fileencode = FileEncode) %>%
#   select(
#     where(
#       ~!all(is.na(.x)) #remove columns of all na
#     )
#   ) %>%
#   select(
#     where(
#       ~!all(str_detect(.x, pattern = "---")) #remove columns containing only all "---"
#     )
#   ) %>%
#   select(-c(`(mbar)`, `(%)`,`('C)...15`,`Ch 1...18`,`Ch1...22`,`Ch1...26`)) %>%
#   rename(Time_hms = `Time (HH:MM:SS)`,
#          LR_s = `Time (s)`,
#          O2_umolL = `Ch1...5`,
#          Temp_C = `Ch 1...9`)
#   )
  
head(O2Data)
```

Reads in O2Data files one after another; skips the header "notes" at the beginning of the data and begins to read each file after HeaderRows. Renames columns so there are no duplicates (.name_repair).

There are multiple functions from baseR ('read.delim'), from Tidyverse ('read_delim') or from data.table ('fread') for reading in files; if one approach fails; try another.
Pipe read files directly to cleaning steps; could do cleaning transforms within 'map_df' as well

# Generate columns from Filename
```{r generate columns from Filename}
O2Data <- O2Data %>%
  mutate(Filename = str_remove(string = Filename, pattern = "../RawData/Optode/"),
         Filename = str_remove(string = Filename, pattern = ".txt"),
         Filename = str_remove(string = Filename, pattern = "caloxy_")) %>%
  separate(Filename, into = c("Run", "FileDateTime", "Project", "CultureID", "Ex_WL", "GrowthLight"), sep = "([\\/\\_])", remove = FALSE)


head(O2Data)
```



Fix column classes
```{r fix column classes}
colnames(O2Data)

O2Data <- type_convert(O2Data) %>%
  mutate(Ex_WL = as.factor(Ex_WL))

head(O2Data)
```

```{r prelim plot}
O2Data %>%
  ggplot() +
  geom_point(aes(x = LR_s, y = O2_umolL)) +
  theme_bw()

O2Data %>%
  filter(Date == "2022-04-06") %>%
  ggplot() +
  geom_point(aes(x = LR_s, y = O2_umolL, colour = Ex_WL)) +
  scale_colour_manual(values = Colours_nm) +
  facet_grid(rows = vars(Ex_WL), cols = vars(CultureID)) +
  coord_cartesian(xlim = c(0,1200)) +
  theme_bw()


```


```{r save O2Data}
saveRDS(O2Data, file.path(DataOut, paste(Project, Run, "O2Data.Rds", sep = "_"), fsep = .Platform$file.sep))
```

