---
title: "O2ImportTidyTutorial"
author:

- Douglas A. Campbell
- Maximilian Berthold
- Laurel Genge
output:
  html_document:
    df_print: paged
    code_folding: hide
    keep_md: yes
    fig_caption: yes
    toc: TRUE
    toc_float: TRUE
csl: plos-one.csl
---

# Introduction
We use an optode to measure [O2] µmol l-1 in suspensions of phytoplankton.
Changes in [O2] reflect (hopefully) oxygen evolution or oxygen consumption by the cell suspension.

# Materials and Methods

This .Rmd Rworkbook imports multiple paralle data files in simple .txt .tsv form exported from FireSting optodes based upon project specific values for variables set by the user.

It tidies and organizes the data.

 
# Set Chunk Options
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

```{r set project variables}

Project <- "FluorO2"

Run <- "SySlCCACaloxy"

FileID <- "caloxy"
DataIn <- file.path("..", "RawData", "Optode", Run)

DataOut <- file.path("..", "ImportData", "Optode")

FileEncode <- "UTF-8"
Delimiter <- "\t"

HeaderRows <- 13
Comment <- "#"

#Set URL for MetaData
MetaDataURL <- "https://docs.google.com/spreadsheets/d/1ZXpwR7Gfto-uRzVdXzMpQF4frbrvMLH_IyLqonFZRSw/edit#gid=0"


```

```{r load libraries} 
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
library(broom)
library(googlesheets4)
library(googledrive)

#library(knitr)
#library(zoo)
#library(tidyquant)
```


```{r set colours}
#Setting a vector of wavelength values, then using it to 'name' a vector of R colour values will allow us to assign colours to wavelengths later
Wavelengths_nm = c(445, 470, 505, 535, 590)
Colours_nm = c("darkblue", "dodgerblue", "darkgreen", "yellowgreen",  "darkorange")


names(Colours_nm) <- Wavelengths_nm
Colours_nm


```

Read in MetaData catalog
```{r load catalog from googlesheet}

gs4_deauth #deauthorizes access to googlesheet

MetaData <- read_sheet(MetaDataURL) %>%
  drop_na(WL) %>%
  mutate(WL = unlist(WL))

# # sheet is read in by sheet ID, obtained from the URL of the sheet.
# # read_sheet sets the type of columns it can't parse to a list.
# # ggplot/dplyr does not work well with a dataframe of lists.
# # In this case WL is set to a list since some values are numbers, some are strings, some are blank.
# # To fix this, first drop all rows missing WL, then unlist.
# # Must first drop NA rows since unlist will collapse NULL lists, then the unlisted WL is a shorter length than original WL column, which mutate doesn't like.
# 
 
 as.data.frame(MetaCatalog)
```

